Intersection Type Algebras

### 2024-08-16 UTA/notes.tex
notes updates

@@

@@

A given set of equations can lead to multiple SR.  These are all equivalent.
\end{document}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}

@@

\newcommand{\types}{\mathbb{T}}

@@

A given set of equations can lead to multiple SR.  These are all equivalent.

The \emph{recursive type entailment problem} is as follows.
Given a set of equations between types $E$ and two types $A$ and $B$,
determine whether $E \vdash A = B$.

The \emph{unification problem} is: Given two types $A$ and $B$,
determine whether there exists a substitution $\sigma$
so that $\vdash A[\sigma] = B[\sigma]$.

The \emph{unification problem up to constraints} is: Given a set of equations $E$,
and two types $A$ and $B$, determine whether there exists a substitution $\sigma$
so that $E \vdash A[\sigma] = B[\sigma]$.

The \emph{general satisfiability problem} is as follows.

Given sets of equations $E_1$, $E_2$, determine whether there exists
a type algebra morphism $h : \types/E_1 \to \types/E_2$.

\end{document}
